---
output: 
    github_document : []
    html_document: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

suppressPackageStartupMessages(library(RLinuxModules))

module("load git/2.21.0")
gitRevision <- function(allcommits=FALSE){
  ## Fetch all commits for a specific file, knitr::current_input() can be NULL
  ## If the filename is omitted, the latest commits will be returned
  shasum <- system(paste("git log --pretty=format:'%h'", knitr::current_input()), intern=TRUE)
  if(!allcommits) {
    shasum <- shasum[1]
  }
  return(shasum)
}

## Capture short sha1sum for latest revision of this Rmd source file
revision <- gitRevision()
```


> The master version of this document is on [Github](https://github.com/Actinidia/eBrida/blob/master/Scripts/ComponentsOfYield/README.Rmd), currently revision
[`r revision`](https://github.com/Actinidia/eBrida/commit/`r revision`) last modified  *`r format(Sys.time(), "%d %b %Y")`*.


# Installation

_Note: Installing Github R packages from private repositories requires generation of a [Github token](https://help.github.com/en/articles/creating-a-personal-access-token-for-the-command-line), then set your $GITUB_PAT environment variable._

```
Sys.setenv(GITHUB_PAT="ba05dd1...d5a87f9")
```

Use remotes to install

```
remotes::install_github("mdavy86/coyparser")
```


# Overview

## Components of Yield

There is a requirement to create functions in R (and perl) to parse
components of yield information for both current and historical formats.

Kris Kramer-Walter has documented the conversion in a word document.


## R code

The following script coy.R is a basis of functions to do the conversion.
This requires a formalized test suite, and potentially the methods should
be part of an S4 object orientated class.

```{r loadCOY}
source("R/coy.R")
ls()
```

## Example 1

The following example was provided;

```{r ex1}
x <- ",0.0574250.240.6.5.00347.21.6L23"

WinterBuds(x)
KingFlowers(x)
LateralFlowers(x)
FloralShoots(x)
VegetShoots(x)
```

## Example 2

Vectorized example;

```{r ex2}
x <- c(",0.0574250.240.6.5.00347.21.6L23", ",1234567.8.9L10")

WinterBuds(x)
KingFlowers(x)
LateralFlowers(x)
FloralShoots(x)
VegetShoots(x)
```


## Tabular conversion

Copying the output headers created in excel;

```{r tabular_ex}
x <- c(",0.0574250.240.6.5.00347.21.6L23", ",1234567.8.9L10")

wideCOY(x)
```



## Sanity checking

The issues appear to be;

1. All input records start with a "," for historical reasons to enforce character conversion
2. All records should contain an "L", or potentially "l" before lateral shoot counts
3. The only valid characters are in the character set [,0-9.Ll]

There are several helper functions;

* coyStart()  - Find malformed records not containing a starting ','
* coyEnd()    - Find malformed records not containing a 'L', or 'l'
* okChars()   - Find all records with illegal characters
* coyChars()  - Report illegal characters
* validateCOY - throw an exception script

```{r sanitychecking}
x <- c("0.0574250.240.6.5.00347.21.6L23", ",1234;567.8.9L10")
coyStart(x)
coyEnd(x)
okChars(x)
coyChars(x)
try(validateCOY(x))
```

## Todo

More information is required to understand and characterize functions for `DeadBuds` and `Blowouts`.

* Collate all background specifications and existing excel conversion scripts
* Convert this to a package namespace
* S4 class with methods?
